Index measures for oak decline severity using phenotypic descriptors

### 2019-12-11 manuscript/manuscript.Rmd

@@

**Estimated crown volume (m^3^)** - estimated volume of crown as an paraboloid proportional to the crown condition. Based on the composite crown volumne from @zarnoch2004 .

@@

>>>>

**Live crown ratio** -

@@

**Composite crown volume (m^3^)** - Estimated volume of crown as an paraboloid proportional to the crown condition. Based on the composite crown volumne from @zarnoch2004 but uses crown condition instead of crown density.

@@

**Composite crown surface area (m^2^)** -

**Crown production efficiency** -
